quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-18 paper-quollr.Rmd
Updated implementation intro

The implementation of `quollr` is designed to be modular, efficient, and easy to extend. The package is organized into a series of logical components that reflect the main stages of the workflow: data preprocessing, model fitting, low-density bin removal, prediction, visualization, and interactive exploration. This modular structure makes the code easier to maintain and allows new features to be added without disrupting the existing functionality.

>>>>

The implementation of `quollr` is designed to be efficient, and easy to extend. The package is organized into a series of logical components that reflect the main stages of the workflow: data preprocessing, model fitting, low-density bin removal, prediction, visualization, and interactive exploration. This package structure makes the code easier to maintain and allows new features to be added without disrupting the existing functionality.

### 2025-10-18 paper-quollr.tex
Updated implementation intro

The implementation of \texttt{quollr} is designed to be modular, efficient, and easy to extend. The package is organized into a series of logical components that reflect the main stages of the workflow: data preprocessing, model fitting, low-density bin removal, prediction, visualization, and interactive exploration. This modular structure makes the code easier to maintain and allows new features to be added without disrupting the existing functionality.

>>>>

The implementation of \texttt{quollr} is designed to be efficient, and easy to extend. The package is organized into a series of logical components that reflect the main stages of the workflow: data preprocessing, model fitting, low-density bin removal, prediction, visualization, and interactive exploration. This package structure makes the code easier to maintain and allows new features to be added without disrupting the existing functionality.
